### 2022-11-22 austins_sim.rmd
Added Error Functions to Graphs

```{r}
library(tidyverse)
library(dplyr)
```

@@

```{r}
names(data)
china <- data %>% filter(location == "China", date < "2020-03-15")
```

@@

@@

>>>>

```{r}
library(tidyverse)
library(dplyr)
library(pracma)
```

@@

```{r}
names(data)
china <- data %>% filter(location == "China", date < "2020-03-20")
china <- subset(china, select = c(date, total_cases, total_deaths))
china <- china %>% mutate(days = 1:n())
```

@@

```{r}
x <- 0:60
func <- function(x) 40000+40000*erf(0.11*x-2)
func2 <- function(x) 1550+1550*erf(0.08*x-2)
```

@@

```{r}
cases_function <- ggplot(china, aes(x = days, y = total_cases)) + 
    geom_line() + 
    stat_function(fun=func, color="#d33636", size=1.5) +
    scale_x_continuous(breaks = seq(0, 60, 1)) +
    labs(title = "Total Cases in China", x = "Days", y = "Total Cases")
fatalities_function <- ggplot(china, aes(x = days, y = total_deaths)) + 
    geom_line() + 
    stat_function(fun=func2, color="#3333e2", size=1.5) +
    scale_x_continuous(breaks = seq(0, 60, 1)) +
    labs(title = "Total Deaths in China", x = "Days", y = "Total Deaths")
```

```{r}
cases_function
fatalities_function
```
